Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-28 appendix.Rmd
Fix formatting for appendix

# restrict floating
knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")

```
Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Phoenix Event Data [@illinoisdatabankIDB-2796521]. After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data. As a results, sextiles were used for these analyses. For comparison, the filtered ICEWS data was also transformed into sextiles.

## CRQA for Phoenix data in sextiles
```{r secondary-crqa-phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

## CRQA for ICEWS data in sextiles
```{r secondary-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

## Windowed CRQA for Phoenix data in sextiles
```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

### Syria as Target
```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}

@@

```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}

@@

```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}

@@

```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}

@@

```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}

@@

```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}

@@

### Syria as Source and Target
```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}

@@

```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}

@@

```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}

@@

## Windowed CRQA for ICEWS data in sextiles
```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

### Syria as Target
```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}

@@

```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}

@@

```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}

@@

```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}

@@

```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}

@@

```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}

@@

### Syria as Source and Target

```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}

@@

```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}

@@

```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}

@@

```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}

>>>>

# restrict floating
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")

# CRQA for Phoenix data in sextiles
```{r secondary-crqa-phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

# CRQA for ICEWS data in sextiles
```{r secondary-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

# Windowed CRQA for Phoenix data in sextiles
```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

```
```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}

@@

# Windowed CRQA for ICEWS data in sextiles
```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

```
```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}

@@

```
```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}

### 2020-05-28 appendix.tex
Fix formatting for appendix

\begin{appendix}
\section{}
Given the inherent issues found in event data sets (Wang, Kennedy,
Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
Peyton, \& Shalmon, 2020). After filtering the data and creating the
count variables for all, positive, and negative events each day, there
was not enough variability to transform the data into deciles for the
target only Phoenix data. As a results, sextiles were used for these
analyses. For comparison, the filtered ICEWS data was also transformed
into sextiles.

\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
\subsection{CRQA for Phoenix data in
sextiles}\label{crqa-for-phoenix-data-in-sextiles}}

@@

\hypertarget{crqa-for-icews-data-in-sextiles}{%
\subsection{CRQA for ICEWS data in
sextiles}\label{crqa-for-icews-data-in-sextiles}}

@@

\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
\subsection{Windowed CRQA for Phoenix data in
sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}

\hypertarget{syria-as-target}{%
\subsubsection{Syria as Target}\label{syria-as-target}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}

\hypertarget{syria-as-source-and-target}{%
\subsubsection{Syria as Source and
Target}\label{syria-as-source-and-target}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
\subsection{Windowed CRQA for ICEWS data in
sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}

\hypertarget{syria-as-target-1}{%
\subsubsection{Syria as Target}\label{syria-as-target-1}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}

\hypertarget{syria-as-source-and-target-1}{%
\subsubsection{Syria as Source and
Target}\label{syria-as-source-and-target-1}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
(2020). \emph{Cline center historical phoenix event data. Cline center
for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
of Illinois at Urbana-Champaign.
\url{https://doi.org/10.13012/B2IDB-0647142_V3}

\leavevmode\hypertarget{ref-wang2016growing}{}%
Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
pains for global monitoring of societal events. \emph{Science},
\emph{353}(6307), 1502--1503.
\end{appendix}

>>>>

\begin{appendix}
\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
\section{CRQA for Phoenix data in
sextiles}\label{crqa-for-phoenix-data-in-sextiles}}

@@

\hypertarget{crqa-for-icews-data-in-sextiles}{%
\section{CRQA for ICEWS data in
sextiles}\label{crqa-for-icews-data-in-sextiles}}

@@

\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
\section{Windowed CRQA for Phoenix data in
sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
\section{Windowed CRQA for ICEWS data in
sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}
\end{appendix}
